Adaptive Exponentiated Gradient

### 2014-01-27 lp/conclusion.tex
done with complete draft

\section{Conclusion} 
\label{sec:conclusion}

>>>>

\section{Discussion} 
\label{sec:conclusion}
We have presented an adaptive exponentiated gradient algorithm, 
which attains regret bounded by the variance of the best expert in retrospect. 
Recently \cite{duchi2011adagrad} have proposed an adaptive subgradient algorithm, 
and it is interesting to compare to their result. They define the quantity 
$\gamma_{T,i} \eqdef \sqrt{\sum_{t=1}^T z_{t,i}^2}$, and obtain regret in terms 
of $\|w\|_{\infty} \sum_{i=1}^n \gamma_{T,i}$. For an appropriately chosen 
$\eta$ our algorithm achieves a similar regret bound on the simplex of
\[ \sqrt{\log(n) \sum_{i=1}^n w_i \gamma_{T,i}^2} \leq \sqrt{\vphantom{\sum_{i=1}^n}\log(n)\|w\|_{\infty}}\sqrt{\sum_{i=1}^n \gamma_{T,i}^2}, \]
which is worse due to the $\log(n)$ factor but better because we pay in terms of 
$\|\gamma_T\|_2$ rather than $\|\gamma_T\|_1$. Our method may therefore perform 
better when the cumulative updates are relatively dense and homogeneous.

When we move beyond the simplex, we obtain a similar regret bound but the 
$\log(n)$ term is replaced by (roughly) a $\log(n) + \|w\|_1\log(\|w\|_1)$ term. 
%The overall regret is then $\sqrt{(\log(n) + \|w\|_1\log(\|w\|_1))\|w\|_{\infty}}\|\gamma_T\|_2$, 
%in comparison to the adagrad regret of $\|w\|_{\infty}\|\gamma_T\|_1$. 
In addition to the $\log(n)$ term that was there before, we now pay for (ignoring 
the $\log(\|w\|_1)$ term) $\sqrt{\|w\|_1\|w\|_{\infty}}$ as opposed to 
$\|w\|_{\infty}$, but are again compensated by measuring $\gamma_T$ in the 
$2$-norm rather than the $1$-norm. In analogy with the preceding paragraph, 
we may expect to perform well when 
the optimal predictor $w$ is sparse but the cumulative squared gradient 
$\gamma_T$ is dense. It would be interesting to perform an empirical comparison 
of the two algorithms to understand how they perform in various settings.

Finally, we think that the idea of treating the regret bound as a quantity to 
itself be optimized in an online fashion is quite interesting. While the bounds 
thus obtained are particularly nice for adaptive exponentiated gradient 
(because we obtain guarantees in terms of the best fixed expert), there are no 
obstacles to applying the same techniques to other settings as well, such 
as trying to minimize $\sum_{t=1}^T \|z_t - m_t\|_*^2$ in the standard mirror 
descent bound. We believe that such ``auxiliary online optimization'' techniques, 
when applied under the optimistic learning framework, have the potential to greatly improve the performance of online learning algorithms.
